\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2021-07-11 manuscript.tex
Updates to R packages including renv; rebuild manuscript

\begin{Schunk}
\begin{Sinput}
> library("hesim")
> library("data.table")
> n_patients <- 1000
> patients <- data.table(
+   patient_id = 1:n_patients,
+   age = rnorm(n_patients, mean = 45, sd = 7),
+   female = rbinom(n_patients, size = 1, prob = .51)
+ )
> 
> states <- data.table(
+   state_id = c(1, 2),
+   state_name = c("Stable", "Progression") 
+ )
> 
> strategies <- data.table(
+   strategy_id = 1:3,
+   strategy_name = c("SOC", "New 1", "New 2"),
+   soc = c(1, 0, 0),
+   new1 = c(0, 1, 0),
+   new2 = c(0, 0, 1)
+ )
> 
> hesim_dat <- hesim_data(
+   strategies = strategies,
+   patients = patients,
+   states = states
+ )
> print(hesim_dat)
\end{Sinput}
\begin{Soutput}
$strategies
   strategy_id strategy_name soc new1 new2
1:           1           SOC   1    0    0
2:           2         New 1   0    1    0
3:           3         New 2   0    0    1

@@

\begin{Schunk}
\begin{Sinput}
> utilitymod <- create_StateVals(utility_tbl, n = n_samples, 
+                                hesim_data = hesim_dat)
> drugcostmod <- create_StateVals(drugcost_tbl, n = n_samples,
+                                 time_reset = TRUE, hesim_data = hesim_dat)
> medcostmod <- create_StateVals(medcost_tbl, n = n_samples,
+                                hesim_data = hesim_dat)
> costmods <- list(Drug = drugcostmod,
+                  Medical = medcostmod)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> onc_pfs_os_soc <- onc_pfs_os[strategy_name == "SOC"]
> fit_pfs_soc_wei <- flexsurvreg(
+   Surv(pfs_time, pfs_status) ~ female,
+   data = onc_pfs_os_soc,
+   dist = "weibull")
> 
> fit_os_soc_wei <- flexsurvreg(
+   Surv(os_time, os_status) ~  female,
+   data = onc_pfs_os_soc,
+   dist = "weibull")
> 
> psmfit_soc_wei <- partsurvfit(
+   flexsurvreg_list(pfs = fit_pfs_soc_wei, os = fit_os_soc_wei),
+   data = onc_pfs_os_soc
+ )
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> x_rr <- as.matrix(transmod_data[, .(soc, new1, new2)])
> rr <- cbind(xbeta(x_rr, params_rr_rng$rr_12),
+             xbeta(x_rr, params_rr_rng$rr_13))
> head(rr) 
\end{Sinput}
\begin{Soutput}
         [,1]      [,2]
[1,] 1.000000 1.0000000
[2,] 1.000000 1.0000000
[3,] 1.000000 1.0000000
[4,] 1.000000 1.0000000
[5,] 0.833283 0.9039595
[6,] 0.833283 0.9039595
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> wtp <- seq(0, 250000, 500) 
> cea_ictstm <- cea(ce_sim_ictstm, dr_costs = .03, dr_qalys = .03, k = wtp)
> cea_pw_ictstm <- cea_pw(ce_sim_ictstm, comparator = 1,
+                         dr_qalys = .03, dr_costs = .03,
+                         k = wtp)
\end{Sinput}
\end{Schunk}

>>>>

\begin{Schunk}
\begin{Sinput}
R> library("hesim")
R> library("data.table")
R> n_patients <- 1000
R> patients <- data.table(
+    patient_id = 1:n_patients,
+    age = rnorm(n_patients, mean = 45, sd = 7),
+    female = rbinom(n_patients, size = 1, prob = .51)
+  )
R> 
R> states <- data.table(
+    state_id = c(1, 2),
+    state_name = c("Stable", "Progression") 
+  )
R> 
R> strategies <- data.table(
+    strategy_id = 1:3,
+    strategy_name = c("SOC", "New 1", "New 2"),
+    soc = c(1, 0, 0),
+    new1 = c(0, 1, 0),
+    new2 = c(0, 0, 1)
+  )
R> 
R> hesim_dat <- hesim_data(
+    strategies = strategies,
+    patients = patients,
+    states = states
+  )
R> print(hesim_dat)
\end{Sinput}
\begin{Soutput}
$strategies
   strategy_id strategy_name soc new1 new2
1:           1           SOC   1    0    0
2:           2         New 1   0    1    0
3:           3         New 2   0    0    1

@@

\begin{Schunk}
\begin{Sinput}
R> utilitymod <- create_StateVals(utility_tbl, n = n_samples, 
+                                 hesim_data = hesim_dat)
R> drugcostmod <- create_StateVals(drugcost_tbl, n = n_samples,
+                                  time_reset = TRUE, hesim_data = hesim_dat)
R> medcostmod <- create_StateVals(medcost_tbl, n = n_samples,
+                                 hesim_data = hesim_dat)
R> costmods <- list(Drug = drugcostmod,
+                   Medical = medcostmod)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> onc_pfs_os_soc <- onc_pfs_os[strategy_name == "SOC"]
R> fit_pfs_soc_wei <- flexsurvreg(
+    Surv(pfs_time, pfs_status) ~ female,
+    data = onc_pfs_os_soc,
+    dist = "weibull")
R> 
R> fit_os_soc_wei <- flexsurvreg(
+    Surv(os_time, os_status) ~  female,
+    data = onc_pfs_os_soc,
+    dist = "weibull")
R> 
R> psmfit_soc_wei <- partsurvfit(
+    flexsurvreg_list(pfs = fit_pfs_soc_wei, os = fit_os_soc_wei),
+    data = onc_pfs_os_soc
+  )
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> x_rr <- as.matrix(transmod_data[, .(soc, new1, new2)])
R> rr <- cbind(xbeta(x_rr, params_rr_rng$rr_12),
+              xbeta(x_rr, params_rr_rng$rr_13))
R> head(rr) 
\end{Sinput}
\begin{Soutput}
         [,1]      [,2]
[1,] 1.000000 1.0000000
[2,] 1.000000 1.0000000
[3,] 1.000000 1.0000000
[4,] 1.000000 1.0000000
[5,] 0.833283 0.9039595
[6,] 0.833283 0.9039595
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> wtp <- seq(0, 250000, 500) 
R> cea_ictstm <- cea(ce_sim_ictstm, dr_costs = .03, dr_qalys = .03, k = wtp)
R> cea_pw_ictstm <- cea_pw(ce_sim_ictstm, comparator = 1,
+                          dr_qalys = .03, dr_costs = .03,
+                          k = wtp)
\end{Sinput}
\end{Schunk}
